Hedonic Price Modelling with Geographically Weighted Regression in Medellin, Colombia

### 2016-07-27 paper/paper_GWR.tex
More literature.

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
% Do not put math or special symbols in the title.
\title{Hedonic Price Modelling with Geographically Weighted Regression in Medellín, Colombia}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%

@@

\subsection{Data and variables}

@@

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\begin{thebibliography}{2}

@@

>>>>

\begin{document}
%
% paper title
% can use linebreaks \\ within to get better formatting as desired
% Do not put math or special symbols in the title.
\title{Hedonic Price Modelling with Geographically Weighted Regression in Medellin, Colombia}
%
%
% author names and IEEE memberships
% note positions of commas and nonbreaking spaces ( ~ ) LaTeX will not break
% a structure at a ~ so this keeps an author's name from being broken across
% two lines.
% use \thanks{} to gain access to the first footnote area
% a separate \thanks must be used for each paragraph as LaTeX2e's \thanks
% was not built to handle multiple paragraphs
%

@@

\subsection{Hedonic pricing variables}

\begin{table}[htb]
\caption{Common variables in literature.}
\label{1234}
\resizebox{\columnwidth}{!}{%
\begin{tabular}{|c|c|c|c|}
Type & Variable & Authors & Notes \\

\subsection{Data}

@@

% can use a bibliography generated by BibTeX as a .bbl file
% BibTeX documentation can be easily obtained at:
% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
% The IEEEtran BibTeX style support page is at:
% http://www.michaelshell.org/tex/ieeetran/bibtex/
%\bibliographystyle{IEEEtran}
% argument is your BibTeX string definitions and bibliography database(s)
%\bibliography{IEEEabrv,../bib/paper}
%
% <OR> manually copy in the resultant .bbl file
% set second argument of \begin to the number of references
% (used to reserve space for the reference number labels box)
\begin{thebibliography}{100}

\bibitem{ansel1}
Anselin, Luc, and Nancy Lozano-Gracia. \emph{Spatial Hedonic Models.} Palgrave Handbook of Econometrics (2009): 1213-250.

\bibitem{ansel2}
 Anselin, Luc, Nancy Lozano-Gracia, Uwe Deichmann, and Somik Lall. \emph{ Access To Water - A Spatial Hedonic Approach Applied To Indian Cities.} Policy Research Working Papers (2008).

\bibitem{ansel3}
Luc Anselin. \emph{Research Infrastructure for Spatial Analysis of Real Estate Markets.} Journal of Housing Research 9.1 (1998)

\bibitem{ansel4}
 Anselin, Luc, and Julie Le Gallo. \emph{Interpolation of Air Quality Measures in Hedonic House Price Models: Spatial Aspects.} Spatial Economic Analysis 1.1 (2006): 31-52.

\bibitem{buffalo}
 Hess, Daniel Baldwin, and Tangerine Maria Almeida. \emph{Impact of Proximity to Light Rail Rapid Transit on Station-area Property Values in Buffalo, New York.} CURS Urban Stud. Urban Studies 44.5 (2007): 1041-068.

\bibitem{can}
Can, Ayse. \emph{The Measurement of Neighborhood Dynamics in Urban House Prices.} Economic Geography 66.3 (1990): 254.

\bibitem{colorado}
 Donovan, G. H., P. A. Champ, and D. T. Butry. \emph{Wildfire Risk and Housing Prices: A Case Study from Colorado Springs.} Land Economics 83.2 (2007): 217-33.

\bibitem{dubin2}
Dubin, Robin A. \emph{Spatial Autocorrelation and Neighborhood Quality.} Regional Science and Urban Economics 22.3 (1992): 433-52. Print.

\bibitem{educ}
Gibbons, Steve. \emph{Paying for Good Neighbours: Estimating the Value of an Implied Educated Community.} Urban Studies 40.4 (2003): 809-33. Print.

@@

\
